hormones

### 2020-02-04 analysis/07_hormones.Rmd
new summary
new files for owen

box <- ggplot(hormones, aes(x = as.numeric(treatment), y = plasma_conc)) +
  geom_boxplot(aes(fill = treatment)) +
  #geom_smooth(aes(color = hormone)) +
  facet_wrap(~hormone, scales = "free_y", nrow = 5) +
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16),
                     labels = alllevels) +
  theme_B3() +
  theme(#strip.text = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA)) +
  labs(y = "plasma conc. (ng/mL)", x = "parental stage")

@@

>>>>

box <- ggplot(hormones, aes(x = as.numeric(treatment), y = plasma_conc)) +
  geom_boxplot(aes(fill = treatment)) +
  #geom_smooth(aes(color = hormone)) +
  facet_wrap(~hormone, scales = "free_y", nrow = 5) +
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16),
                     labels = alllevels) +
  theme_B3() +
  theme(#strip.text = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA)) +
  labs(y = "plasma conc. (ng/mL)", x = "parental stage") +
  scale_fill_manual(values = colorscharmaip)

@@

## summary for owen

```{r}
meanTE <- hormoneswide %>% 
  dplyr::group_by(treatment) %>%
  dplyr::summarise(meanTestosterone = (mean(testosterone, na.rm = TRUE)), 
                   meanEstradiol = mean(estradiol, na.rm = TRUE)) %>%
  dplyr::mutate(meanTestosterone = round(meanTestosterone,2)) %>%
  dplyr::mutate(meanEstradiol = round(meanEstradiol,2)) %>%
  dplyr::filter(treatment %in% charlevels) %>%
  droplevels() %>%
  dplyr::mutate(timepoint = as.numeric(treatment)) %>%
  select(timepoint, treatment, meanTestosterone, meanEstradiol)
meanTE
write.csv("../results/07_meanTE.csv", row.names = F)
```
